Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and correlation with baryon disk properties

### 2019-07-17 Document/paper.tex
caption 5

\begin{figure*}
\begin{center}
\subfloat[DMO simulations.]{\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}}
\subfloat[MHD simulations.]{\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}}
\end{center}
\caption{Axial ratios for all halos in the simulation.
  Left/right panels correspond to DMO/MHD simulations, respectively.
  Triangles (squares) represent the measurements at $R_{200}/16$
  ($R_{200}$) which correspond to physical distances of $14\pm 1$ kpc
  ($230\pm 15$ kpc) respectively.
  Here we can visualize three main trends for the whole halo population.
  First, in DMO simulations halos are rounder in the outskirts
  than in the inner part.
  Second, halos in MHD are rounder than its DMO counterparts.
  Third, halos in MHD are less triaxial in the inner regions than in
  the outskirts}
  \label{fig:triaxiality_plane}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.9\columnwidth]{delta_triaxiality_distro.pdf}
\caption{Cumulative fraction of the changes in the triaxility betwen
  MHD and DM simulations at different radii. 
  At all radii at least $80\%$ of the halos became rounder in the MHD
  simulations. 
  However, the effect is more pronounced at smaller radii.}
\label{fig:delta_triaxial_cumulative}
\end{figure}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{cumulative_alignment_DM.pdf}
\includegraphics[width=1.0\textwidth]{cumulative_alignment_MHD.pdf}
\end{center}
\caption{Cumulative alignment}
\label{fig:cumulative_alignment}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\subfloat[DMO simulations.]{\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}}
\subfloat[MHD simulations.]{\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}}
\end{center}
\caption{Axial ratios for all halos in the simulation.
  Left/right panels correspond to DMO/MHD simulations, respectively.
  Triangles (squares) represent the measurements at $R_{200}/16$
  ($R_{200}$) which correspond to physical distances of $14\pm 1$ kpc
  ($230\pm 15$ kpc) respectively.
  Here we can visualize three main trends for the whole halo population.
  First, in DMO simulations halos are rounder in the outskirts
  than in the inner part.
  Second, halos in MHD are rounder than its DMO counterparts.
  Third, halos in MHD are less triaxial in the inner regions than in
  the outskirts.}
  \label{fig:triaxiality_plane}
\end{figure*}

@@

\begin{figure}
\includegraphics[width=0.9\columnwidth]{delta_triaxiality_distro.pdf}
\caption{
  Cumulative distribution for the change in triaxility $\Delta T=T_{\rm
    MHD}-T_{\rm DMO}$ for the same radii used in Figure
  \ref{fig:triaxial_cumulative}. 
  At the virial radius all the halos become less triaxial in the MHD
  simulations. 
  The change in triaxility becomes stronger in the inner regions of
  the dark matter halo.}
\label{fig:delta_triaxial_cumulative}
\end{figure}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{cumulative_alignment_DM.pdf}
\includegraphics[width=1.0\textwidth]{cumulative_alignment_MHD.pdf}
\end{center}
\caption{Cumulative distribution for the alignments between the
  principal axis of the halo shape and the principal axis of the
  stellar disk in the MHD simulations for radii $\leq 0.5R_{200}$.
  Each panel compares the alingment of the corresponding
  major/middle/minor axis both in the halo and the stellar disk.
  In the upper row the haloes come from the DMO simulation, 
  here the central message is that the shells are aligned to each
  other at every radii.
  In the lower row the haloes come from the MHD simulation and is a
  self-consistent comparison with the disks. 
  In this case the dark matter shells twist and  the degree of the
  halo-disk alignment changes with distance.
  The worst halo-disk alignment happens closer to the disk ($14\pm1$ kpc).
  Interestingly an almost perfect halo-disk alignment happens at an intermediate
  radius of $0.25R_{200}$ ($56\pm 4$kpc); while at a larger
  distance $0.5R_{200}$ the two start to missalign.
}
\label{fig:cumulative_alignment}
\end{figure*}
